---
title: "Line Package User Guide"
author: "Chenzhi Ni"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Line Package User Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)
library(lab4.LiUgroupwork)
```

# Line Package

The "line" package provides a function for linear regression analysis. This vignette demonstrates how to use the package and all its implemented methods.

## Installation and Loading

```{r, eval=FALSE}
# Install the package
# install.packages("lab4.LiUgroupwork")

# Load the package
library(lab4.LiUgroupwork)
```

## Usage Examples

### Loading Data

We will use the built-in 'iris' dataset:

```{r}
data(iris)
head(iris)
```

### Running Linear Regression

Use the 'linreg' function for regression analysis:

```{r}
# Predict Petal Length using Sepal Length
result <- linreg(Petal.Length ~ Sepal.Length, data = iris)
```

### Viewing Results

```{r}
# Print basic results
print(result)

# View detailed summary
summary(result)
```

### Plotting

```{r}
plot(result)
```

### Other Methods

```{r}
# Get coefficients
coef(result)

# Get residuals
residuals(result)

# Get fitted values
fitted(result)
```

### Another Example: faithful Dataset

```{r}
data(faithful)

faithful_model <- linreg(eruptions ~ waiting, data = faithful)

summary(faithful_model)
plot(faithful_model)
```

## Conclusion

This package provides comprehensive linear regression analysis capabilities, including model fitting, result summary, and visualization.
